---
title: "Bayou API Connection"
output: html_notebook
---

```{r}
library(tidyverse)
library(httr2)
library(docopt)
```

Create first customer: 

curl https://staging.bayou.energy/api/v1/customers -XPOST -H "Content-Type: application/json" --data '
{
  "email": "m.scott@dundermifflin.com",
  "utility": "speculoos_power"
}
' -u test_174_b4b7c210bd8595bb624ec66e93b273c2d6485b2060dca91da05c1c2ebb4adea1:

```{r}
bayou_token <- 'test_174_b4b7c210bd8595bb624ec66e93b273c2d6485b2060dca91da05c1c2ebb4adea1'

curl_translate('curl https://staging.bayou.energy/api/v1/customers -XPOST -H \"Content-Type: application/json\" --data \'
{
  \"email\": \"m.scott@dundermifflin.com\",
  \"utility\": \"speculoos_power\"
}
\' -u test_174_b4b7c210bd8595bb624ec66e93b273c2d6485b2060dca91da05c1c2ebb4adea1:')
```


```{r}

request("https://staging.bayou.energy/api/v1/customers") %>% 
  req_method("POST") %>% 
  req_body_raw('{"email" = "m.scott@dundermifflin.com",  "utility" = "speculoos_power"}', "application/json") %>% 
  req_auth_basic("test_174_b4b7c210bd8595bb624ec66e93b273c2d6485b2060dca91da05c1c2ebb4adea1", "") %>% 
  req_perform()

#not working yet

req <- request('https://staging.bayou.energy/api/v1/customers') %>% 
  req_headers(Authorization = paste("Bearer", bayou_token)) %>% 
  req_url_query('utility' = 'speculoos_power', 'email' = 'm.scott@dundermifflin.com')


req_dry_run(req)

resp <- req_perform(req)
resp_json <- resp %>% resp_body_json()
data_df <- as.data.frame(resp_json)
data_df

#api_token <- data_df$token

#api_token

```
{
  "id": 2214,
  "external_id": null,
  "email": "m.scott@dundermifflin.com",
  "first_name": null,
  "last_name": null,
  "phone_number": null,
  "address_line_1": null,
  "address_line_2": null,
  "city": null,
  "state": null,
  "zipcode": null,
  "utility": "speculoos_power",
  "account_number": null,
  "onboarding_link": "https://staging.bayou.energy/companies/145/onboard/a0bf1c4964edaac9fea765d1f0862219d034729f461b8c8a621c7a4075df101f_1703388728_0d8b2bc00098d635c816fce6c651580d13ed3e76b229a9fdf90e4e0a9ac6ece3",
  "has_accepted_terms_on": null
}

Onboard the customer

```{r}
onboarding_link <- 'https://staging.bayou.energy/companies/145/onboard/a0bf1c4964edaac9fea765d1f0862219d034729f461b8c8a621c7a4075df101f_1703388728_0d8b2bc00098d635c816fce6c651580d13ed3e76b229a9fdf90e4e0a9ac6ece3'
```
Done through link

Access customer's data
curl https://staging.bayou.energy/api/v1/customers/2214/bills -u test_174_b4b7c210bd8595bb624ec66e93b273c2d6485b2060dca91da05c1c2ebb4adea1:

```{r}

curl_translate("curl https://staging.bayou.energy/api/v1/customers/2214/bills -u test_174_b4b7c210bd8595bb624ec66e93b273c2d6485b2060dca91da05c1c2ebb4adea1:")

req <- request("https://staging.bayou.energy/api/v1/customers/2214/bills") %>% 
  req_auth_basic(bayou_token, "") 

resp <- req_perform(req)

resp_json <- resp %>% resp_body_json()
data_df <- as.data.frame(resp_json)
data_df
```

```{r}
library(httr)

res <- httr::GET(url = "https://staging.bayou.energy/api/v1/customers/2214/bills", httr::authenticate("test_174_b4b7c210bd8595bb624ec66e93b273c2d6485b2060dca91da05c1c2ebb4adea1", ""))

res

```



